---
title: "Amy Gill's Resume"
author: Amy Gill
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/resume_styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')

# Load csv with position info
position_data <- read_csv('resume_positions.csv')
```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------


- <i class="fa fa-envelope"></i> gill.signals@gmail.com
- <i class="fa fa-github"></i> [github.com/gillsignals](http://github.com/gillsignals)
<!-- - <i class="fa fa-link"></i> [amygill.net](http://amygill.net/) --> 
- <i class="fa fa-phone"></i> (847) 477-3100
- <i class="fa fa-linkedin"></i> [linkedin.com/in/amy-gill-29693244/](https://www.linkedin.com/in/amy-gill-29693244/)



Skills {#skills}
--------------------------------------------------------------------------------

- <i class="fa fa-laptop"></i> **Programming**: R, Bioconductor, Python, GitHub, HTML
- <i class="fa fa-flask"></i> **Laboratory**: Cell culture, western blot, genotyping, qRT-PCR, primer design, flow cytometry, transfection, lentivirus production, mouse husbandry, zebrafish husbandry
- <i class="fa fa-lightbulb-o"></i> **Other**: Science teaching, science writing, data analysis, data visualization, statistics, machine learning, experimental design


Credentials
--------------------------------------------------------------------------------

- <i class="fa fa-chart-area"></i> [HarvardX Data Science Professional Certificate](https://www.edx.org/professional-certificate/harvardx-data-science)
- <i class="fa fa-drivers-license"></i> Professional Educator License (IL): Secondary Biology, Secondary Chemistry


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown). 

The source code is available at [github.com/gillsignals/cv](https://github.com/gillsignals/cv).

See the full version of this CV with links at [amygill.net/cv](http://amygill.net/cv).

Last updated on `r Sys.Date()`.


Main
================================================================================

Amy Gill {#title}
--------------------------------------------------------------------------------
My career goals are to advance personalized cancer therapy with data-driven systems biology and improve quantitative biology education resources. I currently seek a doctoral program to enhance my bioinformatics skills, practice teaching and perform patient-centered research.

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```


Research Experience {data-icon=flask}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'research_positions')
```


:::aside

Peer-reviewed Publications
--------------------------------------------------------------------------------
- [Splicing modulation sensitizes chronic lymphocytic leukemia cells to venetoclax by remodeling mitochondrial apoptotic dependencies](https://www.ncbi.nlm.nih.gov/pubmed/30282833). Ten Hacken E et al. (2018), JCI Insight 3(19).
- [Identification of Novel Protein Expression Changes Following Cisplatin Treatment and Application to Combination Therapy](https://www.ncbi.nlm.nih.gov/pubmed/28902521). Stark AL et al (2017). Journal of Proteome Research, 16(11): 4227-4236.
- [Truncated DNMT3B isoform DNMT3B7 suppresses growth, induces differentiation, and alters DNA methylation in human neuroblastoma.](https://www.ncbi.nlm.nih.gov/pubmed/22815530). Ostler KR et al (2012). Cancer Research 72(18): 4714-23.


Posters and Presentations
--------------------------------------------------------------------------------
- [The role of PRDM1 in protection against radiogenic breast cancer.](https://github.com/gillsignals/science-docs/blob/master/prdm1_talk_140305.pptx) Oral presentation, Dept. Pediatric Hem/Onc, UChicago (2014).
- The role of Blimp1 in protection against ionizing radiation in breast cells. Poster, Biomedical Sciences Retreat, UChicago (2014).
- Systems analysis of cytarabine response and resistance in hematopoietic cells. Poster, Biomedical Sciences Retreat, UChicago (2013).
:::

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'teaching_positions')
```




```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>


")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```


